Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-17 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Corrections sec5

A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} =&
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

@@

Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$ as

@@

\begin{equation} \label{eq_22}

@@

    {\sigma}^{xx} =
    \frac{-1}{4\pi\hbar A} &
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})

@@

    \mel{n,k_x}{

@@

    \qty(

@@

    )

@@

    \qty(
    \vb{G}^{r}_0 (\varepsilon) - \vb{G}^{a}_0 (\varepsilon)
    )

@@

    {n,k_x},

@@

\begin{equation} \label{eq_23}

@@

    {\sigma}^{xx}  = &

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \frac{1}{V_{k_x}^4} \sum_{k_x} \sum_{n}

@@

    \sum_{n_1,n_2,n_3}\\
    \mel{n,k_x}{

@@

    )}

@@

    {n,k_x}.

@@

\begin{equation} \label{eq_24}

@@

  )\vb{T}}

@@

  \qty[
  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
  \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}}

@@

  \qty(
  \frac{1}{\hbar}\varepsilon -
  \frac{1}{\hbar}\varepsilon_{n_1}
  )^2
  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
  }],

@@

\begin{equation} \label{eq_25}

@@

  )\vb{T}}

@@

  \qty[
  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
  \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}}

@@

  \qty(
  \frac{1}{\hbar}\varepsilon -
  \frac{1}{\hbar}\varepsilon_{n}
  )^2
  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
  }].

@@

expressions from Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
\begin{equation} \label{eq_26}

@@

    {\sigma}^{xx}  =
    \frac{-1}{4\pi\hbar A} &
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \sum_{n_1,n_2}

@@

    \qty(\sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}
    \delta_{n_1,n-1})
    \qty[
    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
    \delta_{n_1,n_2}}

@@

    \qty(
    \frac{1}{\hbar}\varepsilon -
    \frac{1}{\hbar}\varepsilon_{n_1}
    )^2
    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
    }] \\

@@

    \qty(\sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
    \delta_{n,n_2-1})
    \qty[
    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})

@@

    \qty(
    \frac{1}{\hbar}\varepsilon -
    \frac{1}{\hbar}\varepsilon_{n}
    )^2
    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
    }],

@@

For the full derivation of electric current operators in quantum Hall system refer to Appendix \ref{appendix_d}.

@@

\begin{equation} \label{eq_27}

@@

    {\sigma}^{xx} =

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})

@@

    \qty(n+1)

@@

    \qty[
    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}

@@

    \qty(
    \frac{1}{\hbar}\varepsilon -
    \frac{1}{\hbar}\varepsilon_{n+1}
    )^2
    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}]^2
    }]
    \qty[
    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}

@@

    \qty(
    \frac{1}{\hbar}\varepsilon -
    \frac{1}{\hbar}\varepsilon_{n}
    )^2
    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}]^2
    }].

@@

\begin{equation} \label{eq_28}
  \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}.

@@

Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in \ref{eq_27} as follows
\begin{equation} \label{eq_29}
    {\sigma}^{xx}   =

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \qty(n+1)
    \qty[
    \frac{\tilde{{\Gamma}}(\varepsilon_{n+1})

@@

    \qty(

@@

    )^2
    + \tilde{{\Gamma}}^2(\varepsilon_{n+1})
    }]
    \qty[
    \frac{\tilde{{\Gamma}}(\varepsilon_{n})

@@

    )^2
    + \tilde{{\Gamma}}^2(\varepsilon_{n})
    }],

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) = \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.

@@

\begin{equation} \label{eq_30}
 -\frac{m_e\omega_0 Ly}{2\hbar} \leq k_x \leq \frac{m_e\omega_0 Ly}{2\hbar}.

@@

\begin{equation} \label{eq_31}
  f(\varepsilon) = \frac{1}{\qty[\exp(\varepsilon - \varepsilon_F)/k_B T]+1},

@@

\begin{equation} \label{eq_32}

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq_29} leads to
\begin{equation} \label{eq_33}

@@

    {\sigma}^{xx}  =
    \frac{e^2}{\hbar}
    \frac{1}{\pi A} &
    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\

@@

    \qty[

@@

        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2

@@

    ]
    \qty[

@@

        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2

@@

    ],

@@

where $X_F = ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$

@@

$\gamma_n = {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.

@@

\begin{equation} \label{eq_34}

@@

    \frac{e^2}{\hbar}
    \frac{1}{\pi A}&

@@

    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\

@@

    ].

>>>>

A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq:22}
  \begin{aligned}
    \sigma^{xx} = &
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
    -\pdv*{f}{\varepsilon }\right) \\
    &  \quad\times
    \tr
    \left\{
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    {j}^x_0
    \left[
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    \right]
    \right\} d\varepsilon,
  \end{aligned}
\end{equation}
where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component. Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarted and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively. These matrices are defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq:23}
    \Pi- \flatfrac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \flatfrac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.

@@

Eq.~(\ref{eq:22}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as

@@

\begin{equation} \label{eq:24}

@@

    \sigma^{xx} =
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
      -\frac{\partial f}{\partial \varepsilon}
    \right)

@@

    \mel{n,k_x}

@@

      \left[

@@

      \right]

@@

      \left[
      \right]

@@

    {n,k_x}
    d\varepsilon,

@@

\begin{equation} \label{eq:25}

@@

    \sigma^{xx}  = &

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
      -\frac{\partial f}{\partial \varepsilon}
    \right)
    \frac{1}{V_{k_x}^4}
    \sum_{k_x} \sum_{n}

@@

    \sum_{n_1,n_2,n_3} \\
    & \quad\times \mel{n,k_x}{

@@

    \right]

@@

    {n,k_x} d\varepsilon.

@@

\begin{equation} \label{eq:26}
  \mel{{n_1,{k_x}_1}}

@@

    \right]\vb{T}

@@

  \frac

@@

    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
    \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}
    \left(
    \flatfrac{\varepsilon}{\hbar} -
    \flatfrac{\varepsilon_{n_1}}{\hbar}
    \right)^2
    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
  },

@@

\begin{equation} \label{eq:27}

@@

  \right]\vb{T}}

@@

  \frac{
    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
    \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}

@@

    \left(
    \flatfrac{\varepsilon }{\hbar}-
    \flatfrac{\varepsilon_{n}}{\hbar}
    \right)^2
    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
  }.

@@

expressions from Eq.~(\ref{eq:26}) and Eq.~(\ref{eq:27}) back into Eq.~(\ref{eq:25}) we obtain
\begin{equation} \label{eq:28}

@@

    \sigma^{xx}  =
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}&
    \left(
    -\frac{\partial f}{\partial \varepsilon}
    \right)
    \frac{1}{V_{k_x}}
    \sum_{k_x} \sum_{n} \sum_{n_1,n_2}

@@

    \left(
    \sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}\delta_{n_1,n-1}
    \right)
    \left\{
    \frac

@@

      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
      \delta_{n_1,n_2}
      \left(
      \flatfrac{\varepsilon}{\hbar} -
      \flatfrac{\varepsilon_{n_1}}{\hbar}
      \right)^2
      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
    \right\} \\

@@

    \left(
    \sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
    \delta_{n,n_2-1}
    \right)
    \left\{
    \frac{
      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})

@@

      \left(
      \flatfrac{\varepsilon }{\hbar}-
      \flatfrac{\varepsilon_{n}}{\hbar}
      \right)^2
      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
    \right\}  d\varepsilon,

@@

For the full derivation of electric current operators in a quantum Hall system, refer to Appendix \ref{appendix_d}.

@@

\begin{equation} \label{eq:29}

@@

    \sigma^{xx} =

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
    -\frac{\partial f}{\partial \varepsilon}\right)

@@

    (n+1)

@@

    \left\{
    \frac
      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}

@@

      \left(
      \flatfrac{\varepsilon}{\hbar} -
      \flatfrac{\varepsilon_{n+1}}{\hbar}
      \right)^2
      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}\right]^2
    \right\}
    \left\{
    \frac{
      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}

@@

      \left(
      \flatfrac{\varepsilon }{\hbar}-
      \flatfrac{\varepsilon_{n}}{\hbar}
      \right)^2
      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}\right]^2
    \right\}
    d\varepsilon.

@@

\begin{equation} \label{eq:30}
  \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll} =
  -2\text{Im} \left[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}\right]^{ll}.

@@

Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
\begin{equation} \label{eq:31}
    \sigma^{xx}   =

@@

    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
    \left(
      -\frac{\partial f}{\partial \varepsilon}
    \right)
    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n} (n+1)
    \left[
    \frac{\widetilde{{\Gamma}}(\varepsilon_{n+1})

@@

    \left(

@@

    \right)^2
    + \widetilde{{\Gamma}}^2(\varepsilon_{n+1})
    \right]
    \left[
    \frac{\widetilde{{\Gamma}}(\varepsilon_{n})

@@

    \right)^2
    + \widetilde{{\Gamma}}^2(\varepsilon_{n})
    \right]
    d\varepsilon,

@@

with $\widetilde{{\Gamma}}(\varepsilon_n,k_x) = \left[\flatfrac{\hbar}{2\tau(\varepsilon_n,k_x)}\right]^{00}$. Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\widetilde{{\Gamma}}(\varepsilon_n,k_x)$ terms. Subsequently, we can get the sum over available momentum in $x$-direction.

@@

\begin{equation} \label{eq:32}
 -\flatfrac{m_e\omega_0 Ly}{(2\hbar)} \leq k_x \leq \flatfrac{m_e\omega_0 Ly}{(2\hbar)}.

@@

\begin{equation} \label{eq:33}
  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},

@@

\begin{equation} \label{eq:34}

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq:31} leads to
\begin{equation} \label{eq:35}

@@

    \sigma^{xx}  =
    \frac{e^2}{\pi\hbar A}
    \sum_{n} &
    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\

@@

    \left[

@@

        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2

@@

    \right]
    \left[

@@

        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2

@@

    \right],

@@

where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$

@@

$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.

@@

\begin{equation} \label{eq:36}

@@

    \frac{e^2}{\pi\hbar A} &

@@

    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\

@@

    \right].
